Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus (Extended Version)

### 2025-04-10 paper/paper.tex
a more human data availability statement
clean up the acks

\begin{acks}
  This material is based upon work supported by the Air Force Office of
  Scientific Research under Grant No.~\grantnum{}{FA9550-23-1-0760}.  Any
  opinions, findings and conclusions or recommendations expressed in this
  material are those of the authors and do not necessarily reflect the views of
  the U.S. Department of Defense.
  %
  This work is also supported by the ERC Consolidator Grant BLAST and the ARIA
  programme on Safeguarded AI.  Any opinions, findings, and conclusions or
  recommendations expressed in this material are those of the author and do not
  necessarily reflect the views of the National Science Foundation, the European
  Research Council or the Advanced Research and Invention Agency.
\end{acks}

>>>>

\begin{acks}
  This material is based upon work supported by the Air Force Office of
  Scientific Research under Grant No.~\grantnum{}{FA9550-23-1-0760}, the ERC
  Consolidator Grant BLAST and the ARIA programme on Safeguarded AI. Any
  opinions, findings, and conclusions or recommendations expressed in this
  material are those of the authors and do not necessarily reflect the views of
  the U.S. Department of Defense, the European Research Council or the Advanced
  Research and Invention Agency.
\end{acks}

\section*{Data-Availability Statement}
The Agda implementation of \theoryabbv and the formalization of our proofs are archived on Zenodo \cite{schaefer_2025_15049780} and the source code is available \href{https://github.com/maxsnew/grammars-and-semantic-actions/tree/PLDI25Artifact}{on GitHub}.
